Pulmonary acini exhibit complex changes during postnatal rat lung development

### 2021-07-16 manuscript.tex
Add explanatory sentence at the end [ci skip]
This build is based on
https://github.com/habi/acinar-analysis-manuscript/commit/e309b5aa0a885f3ac74bf76ec2b2ebacfc38d176.

This commit was created by the following CI build and job:
https://github.com/habi/acinar-analysis-manuscript/commit/e309b5aa0a885f3ac74bf76ec2b2ebacfc38d176/checks
https://github.com/habi/acinar-analysis-manuscript/runs/1036774786

A preprint of this manuscript is available on \emph{bioRxiv} with the DOI \href{https://doi.org/10.1101/786681}{10.1101/786681}.
It has been submited to \href{https://journals.plos.org/plosone/}{\emph{PLOS ONE}}.
The manuscript \href{https://github.com/habi/acinar-analysis-manuscript/compare/5e778036e316c47b8bac4ce50086b191a7e3707a...99ffa8bd678eeecd9115c32def3159b50a367a33}{has been updated} since submission.

This manuscript
(\href{https://habi.github.io/acinar-analysis-manuscript/v/99ffa8bd678eeecd9115c32def3159b50a367a33/}{permalink})
was automatically generated
from \href{https://github.com/habi/acinar-analysis-manuscript/tree/99ffa8bd678eeecd9115c32def3159b50a367a33}{habi/acinar-analysis-manuscript@99ffa8b}
on July 15, 2021.

@@

\begin{itemize}
\item
  \textbf{David Haberthür}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3388-9187}{0000-0003-3388-9187}
  · \href{mailto:haberthuer@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(99ffa8b)}{haberthuer@ana.unibe.ch}
  · \includegraphics{images/github.svg}
  \href{https://github.com/habi}{habi}
  · \includegraphics{images/twitter.svg}
  \href{https://twitter.com/habi}{habi}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Eveline Yao}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Sébastien F. Barré}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Tiziana P. Cremona}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-0061-9578}{0000-0003-0061-9578}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Stefan A. Tschanz}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3880-4437}{0000-0003-3880-4437}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Johannes C. Schittny}✉
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-4025-3961}{0000-0003-4025-3961}
  · \href{mailto:schittny@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(99ffa8b)}{schittny@ana.unibe.ch}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\end{itemize}

@@

Our aim was to understand the size distribution of the acini during lung development including the contribution of the rather irregular shape of the alveoli.
The observed range \emph{de}creased during postnatal lung development by a factor of 6--7, which represents an unexpected result.
The obtained data is essential for further investigations, like the influence of the acinar size on ventilation and gas-washout, or the influence of the irregular alveolar shape on particle deposition inside individual acini.
Ongoing work (unpublished results and {[}\protect\hyperlink{ref-eb0gk6VO}{13}{]}) is using a computational fluid dynamics model to simulate exactly this influence.

>>>>

A preprint of this manuscript is available on \emph{bioRxiv} with the DOI \href{https://doi.org/10.1101/786681}{10.1101/786681}.
It has been submited to \href{https://journals.plos.org/plosone/}{\emph{PLOS ONE}}.
The manuscript \href{https://github.com/habi/acinar-analysis-manuscript/compare/5e778036e316c47b8bac4ce50086b191a7e3707a...e309b5aa0a885f3ac74bf76ec2b2ebacfc38d176}{has been updated} since submission.

This manuscript
(\href{https://habi.github.io/acinar-analysis-manuscript/v/e309b5aa0a885f3ac74bf76ec2b2ebacfc38d176/}{permalink})
was automatically generated
from \href{https://github.com/habi/acinar-analysis-manuscript/tree/e309b5aa0a885f3ac74bf76ec2b2ebacfc38d176}{habi/acinar-analysis-manuscript@e309b5a}
on July 16, 2021.

@@

\begin{itemize}
\item
  \textbf{David Haberthür}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3388-9187}{0000-0003-3388-9187}
  · \href{mailto:haberthuer@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(e309b5a)}{haberthuer@ana.unibe.ch}
  · \includegraphics{images/github.svg}
  \href{https://github.com/habi}{habi}
  · \includegraphics{images/twitter.svg}
  \href{https://twitter.com/habi}{habi}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Eveline Yao}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Sébastien F. Barré}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Tiziana P. Cremona}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-0061-9578}{0000-0003-0061-9578}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Stefan A. Tschanz}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3880-4437}{0000-0003-3880-4437}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Johannes C. Schittny}✉
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-4025-3961}{0000-0003-4025-3961}
  · \href{mailto:schittny@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(e309b5a)}{schittny@ana.unibe.ch}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\end{itemize}

@@

Our aim was to understand the size distribution of the acini during lung development including the contribution of the rather irregular shape of the alveoli.
The observed range \emph{de}creased during postnatal lung development by a factor of 6--7, which represents an unexpected result.
The obtained data is essential for further investigations, like the influence of the acinar size on ventilation and gas-washout, or the influence of the irregular alveolar shape on particle deposition inside individual acini.
Ongoing work (unpublished results and {[}\protect\hyperlink{ref-eb0gk6VO}{13}{]}) is using a computational fluid dynamics model to simulate exactly this influence.
In particular, the washout time increases with increasing acinar size, acinar size distribution, and compliance.
